cvx-flats

### 2020-05-15 neurips-20/cvx-flats-statements.tex
touching up prop 1
Still confused on def 5 but brain is fried for the day.  Will come back before monday meeting.

\newcommand{\risk}[1]{\underline{#1}}
\newcommand{\inprod}[2]{\langle #1, #2 \rangle}
\newcommand{\toto}{\rightrightarrows}

@@

%\raf{Issues with the definition:
%\begin{enumerate}
%\item Good to clarify $d:\R\times\R\to\reals_+$ -- done
%\item We have two $d$'s so we'll need a new letter... -- changed to $\mu$
%\item $D_X$ is not defined, but I got it -- clarified it was the marginal distribution
%\item You can't take an expectation over $\R$ values (not necessarily a subset of a vector space) and want the expectation over $X$ on the outside
%\end{enumerate}
%At this point I lost the thread. It looks like you're missing the hypothesis function, and $\Gamma(D)$ doesn't seem to type check -- but perhaps $\Gamma(D)$ was meant to depend on $X$ and be the hypothesis? -- and the implication also seems backwards.}
\begin{definition}[Consistent: property]
	A loss $L : \R \times \Y \to \reals$ and link $\psi : \R' \to \R$ pair $(L, \psi)$ is \emph{$\mu$-consistent with respect to a property} $\gamma: \simplex \toto \R'$ for a distance $\mu:\R \times \R \to \reals_+$ if, for all $D$ over $\X \times \Y$ with marginal distributions $D_x$, and sequences of properties $\{\gamma_m: \simplex \toto \R'\} \to \gamma$, we observe
	\begin{equation}
	\E_{(X,Y) \sim D} L( \psi \circ \gamma_m(D_X), Y) \to \E_{(X,Y) \sim D} L(f(X), Y) \implies \E_X \mu(\psi \circ \gamma_m(D_X), f(X)) \to 0~,~
	\end{equation}
	where $f = \arginf_{f^* \mathrm{msbl}} \E_{(X,Y) \sim D} L(f^*(X), Y)$.
\end{definition}

@@

%\begin{proposition}
%	A surrogate link pair $(L, \psi)$ is consistent with respect to a loss $\ell$ if and only if it is consistent with respect to the property elicited by $\gamma := \prop{\ell}$.
%\end{proposition}
%\begin{proof}
%	$\implies:$ 
%	If $(L, \psi)$ is consistent with respect to $\ell$, then for all $x \in \X$ with $p = Pr[Y|X]$, we have $L(u; p) \to \inf_{u'} L(u';p) \implies \ell(\psi(u); p) \to \inf_{u'} \ell(\psi(u');p)$.
%	As $\inf_{u'} L(u';p) = L(\Gamma(p); p)$, we then have $L(\Gamma(p); p) - L(u;p) \to 0 \implies \ell(\psi(\Gamma(p)); p) - \ell(\psi(u);p) \to 0$.
%	If $\gamma: p \mapsto \psi(\Gamma(p))$ for all $p \in \simplex$, then we have consistency with respect to $\gamma$, as $\zeta$ being the identity satisfies the requirements on $\zeta$ and yields the bound as the convergence yields $0 \leq 0$ for all $p \in \simplex$.
%	
%	To see $\gamma = \psi \circ \Gamma$, consider that for all $p \in \simplex$, we have $\arginf_{u \in \reals^d} L(u;p) = \arginf_{u \in \reals^d} \ell(\psi(u); p)$ as a corollary of consistency with respect to $\ell$, which implies the statement.
%	
%	$\impliedby:$ 
%	If $(L, \psi)$ is consistent with respect to $\gamma$, then there is a monotonic function $\zeta:\reals \to \reals$ that is continuous at $0$ with $\zeta(0) = 0$ such that, for all $p \in \simplex$, we have $\ell( \psi(u); p) - \ell(\gamma(p); p)  \leq \zeta \left(  L(u;p) - L(\Gamma(p); p) \right)$.
%	
%	As this is true for all $p = Pr[Y|X] \in \simplex$, this also holds in expectation over $X$.
%	This gives the excess risk bound being satisfied, which has been shown implies consistency with respect to $\ell$.\jessiet{In Hari abstain paper, but might be worth proving it here, given the subtleties of consistency definitions...}
%\end{proof}

\begin{definition}[Calibrated]\label{def:calibrated-general}
	A loss $L:\reals^d \times \Y \to \reals$ is \emph{calibrated} with respect to a loss $\ell : \R \times \Y \to \reals$ eliciting the property $\gamma$ if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $p \in \simplex$, there exists a function $\zeta : \reals_+ \to \reals_+$ with $\zeta$ continuous at $0^+$ and $\zeta(0) = 0$ such that for all $u \in \reals^d$, we have
	\begin{equation}\label{eq:calibrated-general}
	\ell( \psi(u); p) - \ell(\gamma(p); p)  \leq \zeta \left(  L(u;p) - L(\Gamma(p); p) \right)~.~
	\end{equation}
\end{definition}
\begin{definition}[Calibrated: Finite predictions]\label{def:calibrated-finite}
	Let $\ell : \R \times \Y \to \reals_+$ be a discrete loss eliciting the property $\gamma$.
	A surrogate loss $L : \reals^d \times \Y \to \reals_+$  and link $\psi:\reals^d \to \R$ pair $(L, \psi)$ is \emph{calibrated} with respect to $\ell$ if 
	\begin{equation}\label{eq:calibration}
	\forall p \in \simplex: \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} L(u;p) > \inf_{u \in \reals^d} L(u;p)~.~
	\end{equation}
\end{definition}

@@

\jessie{Should this also be a lemma instead of a proposition?}
\begin{proposition}\label{prop:consistent-implies-calibrated}
	If a loss and link $(L, \psi)$ are consistent with respect to a loss $\ell$, then they are calibrated with respect to $\ell$.
	\jessiet{Probably appendix later.}
\end{proposition}
\begin{proof}
	Let $\gamma$ be the property elicited by $\ell$.
	Suppose $(L,\psi)$ is not calibrated with respect to $\ell$; we will show they are not consistent with respect to $\ell$ either.
	$(L, \psi)$ not calibrated with respect to $\ell$ means that there is some distribution $p \in \simplex = D_x$ for some $x \in \X$ such that there is no function $\zeta : \reals_+ \to \reals_+$ with $\zeta(0) = 0$ and continuous at $0^+$ such that, for all $u \in \reals^d$, we have $\ell(\psi(u); p) - \ell(\gamma(p);p) \leq \zeta(L(u;p) - L(\Gamma(p);p))$. 
	In other words, for all $\zeta$ satisfying the assumptions, we have $\ell(\psi(u); p) - \ell(\gamma(p);p) > \zeta(L(u;p) - L(\Gamma(p);p))$.

	In particular, there must exist a sequence $\{u_m\} \to \Gamma(p)$ so that $\psi(u_m) \not \in \gamma(p)$ for all $m$.
	Now consider the data distribution $D$ that has a point mass on some $x \in \X$, where $p = D_x$.
	Moreover, let $f_m$ be any sequence of functions with $f_m(x) = u_m$ for all $m$.
	We then have $L(f_m(x); p) \to L(\Gamma(p);p)$, so $\lim_{m \to \infty}\zeta(L(u;p) - L(\Gamma(p);p)) \to 0$.
	This gives $\ell(\psi(u);p) > \ell(\gamma(p);p) + \epsilon$ for some $\epsilon \to 0$, which implies $\ell(\psi(u_m); p) \not \to \ell(\gamma(p);p)$; thus, we do not have consistency.
	Therefore, if $(L, \psi)$ are consistent with respect to $\ell$, they are also calibrated with respect to $\ell$.

@@

\begin{lemma}\label{lem:calib-implies-indir}
	If a surrogate and link $(L, \psi)$ are calibrated with respect to a loss $\ell:\R \times\Y \to \reals$, then $L$ indirectly elicits the property $\gamma := \prop{\ell}$.
\end{lemma}
\begin{proof}
	Let $\Gamma$ be the unique property directly elicited by $L$, and fix $p \in \simplex$ with $u$ such that $p \in \Gamma_u$.
	As $p \in \Gamma_u$, then $L(u;p) - L(\Gamma(p); p) = 0$, and $\zeta(0) = 0$, we observe the bound $\ell(\psi(u); p) \leq \ell(\gamma(p); p)$.
	We also have $\ell(\psi(u); p) \geq \ell(\gamma(p); p)$ by definition of $\gamma$, so we must have $\ell(\psi(u);p) = \ell(\gamma(p); p)$, and therefore, $p \in \gamma_{\psi(u)}$.
	Thus, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, so $L$ indirectly elicits $\gamma$.
\end{proof}

@@

If we are just given the property $\gamma$ without a loss, assume that we have a sequence of properties $\{\gamma_m\} \to \gamma$ such that $\E_{(X,Y) \sim D} L( \psi \circ \gamma_m(D_X), Y) \to \E_{(X,Y) \sim D} L(f(X), Y)$, where $f$ minimizes $E_D L(f^*(X), Y)$ over measurable functions $f^*$.
We must then have $\E_X \mu(\gamma_m(D_X), f(X)) \to 0$ by consistency.
As in the proof of Proposition~\ref{prop:consistent-implies-calibrated}, this must be true for all $D_x$ for $x \in \X$, so we can abstract to distributions over $\simplex$.
Now, by consistency, we have the expected losses converging implies $\{\psi \circ \gamma_m\}$ is converging toward the optimal hypothesis for all possible inputs $x \in \X$.

Let $\Gamma$ be the property directly elicited by $L$.
We have $\Gamma(D_x) = f(x)$ for all $x \in \X$, so we can see that the precedent being true implies $\mu(\psi \circ \gamma_m(p), \Gamma(p)) \to 0$ for all $p\in \simplex$.
As $\mu$ is a distance\jessiet{Maybe need $\mu$ continuous in $\R^2$?}, $\mu(\psi \circ \gamma(p), \Gamma(p)) = 0$ for all $p \in \simplex$, which implies $\Gamma = \psi \circ \gamma$ as $\mu$ is a distance.
Therefore, $L$ must indirectly elicit the property $\gamma = \lim_{m \to \infty} \{\gamma_m\}$ via the link $\psi$.
\end{proof}

@@

\newpage
\appendix
\section{Omitted proofs}
\begin{proposition}
	When $\R$ is finite and $L$ continuous in $\reals^d$, calibration of a property via Definition~\ref{def:calibrated-general} implies calibration via Definition~\ref{def:calibrated-finite}.
\end{proposition}
\begin{proof}
	Let $\Gamma$ be the property elicited by $L$.
	We prove the contrapositive; if $(L, \psi)$ is not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then it is not calibrated via Definition~\ref{def:calibrated-general} either.

	Suppose there was a distribution $p \in \simplex$ and sequence $\{u_m\} \to u$ so that $\psi(u_m) \not \to \gamma(p)$ but $L(u_m;p) \to L(\Gamma(p);p)$.
	We would then have $\inf_{u : \psi(u) \not \in \gamma(p)} L(u;p) = \inf_{u} L(u;p)$.

	We want to show that there is no $\zeta:\reals_+ \to \reals_+$ continuous at $0^+$ with $\zeta(0) = 0$ so that 
	\begin{align*}
	\ell(\psi(u);p) - \ell(\gamma(p);p) \leq \zeta(L(u;p) - L(\Gamma(p); p))
	\end{align*}
	for all $u \in \reals^d$.
	We show that if this bound is satisfied, one of the two conditions on $\zeta$ (continuity at $0^+$ and $\zeta(0) = 0$) must be violated.

	Fix $x \in \X$ and take $u_m = f_m(x)$ \jessie{...}

	First, suppose that $\zeta$ is continuous at $0^+$ and the bound is satisfied.
	Then for the sequence $\{u_m\} \to \Gamma(p)$, we have 
	\begin{align*}
	\lim_{m \to \infty}\ell(\psi(u_m); p) - \ell(\gamma(p);p)&\leq \lim_{m \to \infty} \zeta(L(u_m; p) - L(\Gamma(p);p))\\
	\lim_{m \to \infty}\ell(\psi(u_m) ; p) &\leq \ell(\gamma(p);p) + \lim_{m \to \infty} \zeta(L(u_m; p) - L(\Gamma(p);p))\\
	\lim_{m \to \infty}\ell(\psi(u_m) ; p) &\leq \ell(\gamma(p);p) + \lim_{\epsilon \to 0^+} \zeta(\epsilon)
	\end{align*}
	and the last inequality can only happen if $\lim_{\epsilon \to 0^+} \zeta(\epsilon) = c > 0$, and by continuity of $\zeta$, we then have $\lim_{\epsilon \to 0} \zeta(\epsilon) = \zeta(0) = c > 0$.

	Now, suppose $\zeta(0) = 0$, and take the sequence $\{u_m\} \to \Gamma(p)$ where $\psi(u_m) \neq \gamma(p)$ for all $m$.	
	We have 
	\begin{align*}
	\lim_{m \to \infty}\ell(\psi(u_m); p) - \ell(\gamma(p);p)&\leq \lim_{m \to \infty} \zeta(L(u_m; p) - L(\Gamma(p);p))\\
	\lim_{m \to \infty}\ell(\psi(u_m); p) &\leq \ell(\gamma(p);p) +  \lim_{\epsilon \to 0^+} \zeta(\epsilon)\\
%	\ell(\psi(\Gamma(p)); p) - \ell(\gamma(p);p)&\leq \zeta(L(\Gamma(p); p) - L(\Gamma(p);p))\\
%	\ell(\psi(\Gamma(p)); p) - \ell(\gamma(p);p)&\leq \zeta(0)\\
%	\ell(\psi(\Gamma(p)); p) &\leq \zeta(0) + \ell(\gamma(p); p)\\
%	\ell(\psi(\Gamma(p)); p) &\leq \ell(\gamma(p); p)~.~
	\end{align*}
	As $\ell(\psi(u_m); p)> \ell(\gamma(p); p)$ (since $\R$ is finite) for all $m$, we then observe that $\lim_{\epsilon \to 0^+} \zeta(\epsilon) = c > 0$.
	However, since $\zeta(0) = 0$, we violate continuity of $\zeta$ at $0^+$.
\end{proof}

>>>>

\newcommand{\risk}[1]{#1^*}
\newcommand{\inprod}[2]{\langle #1, #2 \rangle}
\newcommand{\toto}{\rightrightarrows}

@@

%\raf{Issues with the definition:
%\begin{enumerate}
%\item Good to clarify $d:\R\times\R\to\reals_+$ -- done
%\item We have two $d$'s so we'll need a new letter... -- changed to $\mu$
%\item $D_X$ is not defined, but I got it -- clarified it was the marginal distribution
%\item You can't take an expectation over $\R$ values (not necessarily a subset of a vector space) and want the expectation over $X$ on the outside
%\end{enumerate}
%At this point I lost the thread. It looks like you're missing the hypothesis function, and $\Gamma(D)$ doesn't seem to type check -- but perhaps $\Gamma(D)$ was meant to depend on $X$ and be the hypothesis? -- and the implication also seems backwards.}
\begin{definition}[Consistent: property]
	Let $\{f_m: \X \to \R\}$ be a sequence of hypothesis functions.
	A loss $L : \R \times \Y \to \reals$ and link $\psi : \R \to \R'$ pair $(L, \psi)$ is \emph{$\mu$-consistent with respect to a property} $\gamma: \simplex \toto \R'$ for a distance $\mu:\R \times \R \to \reals_+$ if, for all $D$ over $\X \times \Y$ with marginal distributions $D_x$, and 
	\begin{equation}
	\E_{(X,Y) \sim D} L(\psi \circ f_m(X), Y) \to \E_{(X,Y) \sim D} L( \gamma(D_X), Y) \implies \E_X \mu(\gamma(D_X), \psi \circ f_m(X)) \to 0~.~
	\end{equation}
	If $\mu$ has a set as input, define $\mu(S_1, S_2) = \inf_{s_1 \in S_1, s_2 \in S_2} \mu(s_1, s_2)$.
\end{definition}

@@

%\begin{proposition}
%	A surrogate link pair $(L, \psi)$ is consistent with respect to a loss $\ell$ if and only if it is consistent with respect to the property elicited by $\gamma := \prop{\ell}$.
%\end{proposition}
%\begin{proof}
%	$\implies:$ 
%	If $(L, \psi)$ is consistent with respect to $\ell$, then for all $x \in \X$ with $p = Pr[Y|X]$, we have $L(u; p) \to \inf_{u'} L(u';p) \implies \ell(\psi(u); p) \to \inf_{u'} \ell(\psi(u');p)$.
%	As $\inf_{u'} L(u';p) = \risk{L}(p)$, we then have $\risk{L}(p) - L(u;p) \to 0 \implies \ell(\psi(\Gamma(p)); p) - \ell(\psi(u);p) \to 0$.
%	If $\gamma: p \mapsto \psi(\Gamma(p))$ for all $p \in \simplex$, then we have consistency with respect to $\gamma$, as $\zeta$ being the identity satisfies the requirements on $\zeta$ and yields the bound as the convergence yields $0 \leq 0$ for all $p \in \simplex$.
%	
%	To see $\gamma = \psi \circ \Gamma$, consider that for all $p \in \simplex$, we have $\arginf_{u \in \reals^d} L(u;p) = \arginf_{u \in \reals^d} \ell(\psi(u); p)$ as a corollary of consistency with respect to $\ell$, which implies the statement.
%	
%	$\impliedby:$ 
%	If $(L, \psi)$ is consistent with respect to $\gamma$, then there is a monotonic function $\zeta:\reals \to \reals$ that is continuous at $0$ with $\zeta(0) = 0$ such that, for all $p \in \simplex$, we have $\ell( \psi(u); p) - \ell(\gamma(p); p)  \leq \zeta \left(  L(u;p) - L(\Gamma(p); p) \right)$.
%	
%	As this is true for all $p = Pr[Y|X] \in \simplex$, this also holds in expectation over $X$.
%	This gives the excess risk bound being satisfied, which has been shown implies consistency with respect to $\ell$.\jessiet{In Hari abstain paper, but might be worth proving it here, given the subtleties of consistency definitions...}
%\end{proof}

\begin{definition}[Calibrated]\label{def:calibrated-general}
	A loss $L:\reals^d \times \Y \to \reals$ is \emph{calibrated} with respect to a loss $\ell : \R \times \Y \to \reals$ eliciting the property $\gamma$ if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $p \in \simplex$, there exists a function $\zeta : \reals_+ \to \reals_+$ with $\zeta$ continuous at $0^+$ and $\zeta(0) = 0$ such that for all $u \in \reals^d$, we have
	\begin{equation}\label{eq:calibrated-general}
	\ell( \psi(u); p) - \ell(\gamma(p); p)  \leq \zeta \left(  L(u;p) - \risk{L}(p) \right)~.~
	\end{equation}
\end{definition}
\begin{definition}[Calibrated: Finite predictions]\label{def:calibrated-finite}
	Let $\ell : \R \times \Y \to \reals_+$ be a discrete loss eliciting the property $\gamma$.
	A surrogate loss $L : \reals^d \times \Y \to \reals_+$  and link $\psi:\reals^d \to \R$ pair $(L, \psi)$ is \emph{calibrated} with respect to $\ell$ if 
	\begin{equation}\label{eq:calibration}
	\forall p \in \simplex: \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} L(u;p) > \inf_{u \in \reals^d} L(u;p)~.~
	\end{equation}
\end{definition}

@@

\jessie{Should this also be a lemma instead of a proposition?}
\begin{proposition}\label{prop:consistent-implies-calibrated}
	If a (continuous) loss and link $(L, \psi)$ are consistent with respect to a loss $\ell$, then they are calibrated with respect to $\ell$.
	\jessiet{Probably appendix later.}
\end{proposition}
\begin{proof}
	Let $\gamma$ be the property elicited by $\ell$.
	Suppose $(L,\psi)$ is not calibrated with respect to $\ell$; we will show they are not consistent with respect to $\ell$ either.
	$(L, \psi)$ not calibrated with respect to $\ell$ means that there is some distribution $p \in \simplex$ such that there is no function $\zeta : \reals_+ \to \reals_+$ with $\zeta(0) = 0$ and continuous at $0^+$ such that, for all $u \in \reals^d$, we have $\ell(\psi(u); p) - \risk{\ell}(p) \leq \zeta(L(u;p) - \risk{L}(p))$. 
	In other words, for all $\zeta$ satisfying the assumptions, we have $\ell(\psi(u); p) - \risk{\ell}(p) > \zeta(L(u;p) - \risk{L}(p))$ for some $u \in \reals^d$.
	In particular, there must exist a sequence $\{u_m\}$ so that $L(u_m;p) \to \risk{L}(p)$.

	Now consider the data distribution $D$ that has a point mass on some $x \in \X$, where $p = D_x$.
	Moreover, let $f_m$ be any sequence of functions with $f_m(x) = u_m$ for all $m$.
	We then have $L(f_m(x); p) = L(u_m; p) \to \risk{L}(p)$, so $\lim_{m \to \infty}\zeta(L(u_m;p) - \risk{L}(p)) \to 0$.
	This gives $\ell(\psi(u_m);p) > \risk{\ell}(p) + \epsilon_m$ for all $m$, and $\epsilon_m \to 0$.
	We can now observe that we do not have consistency as $\ell(\psi(u_m); p) \not \to \risk{\ell}(p)$.
	Therefore, if $(L, \psi)$ are consistent with respect to $\ell$, they are also calibrated with respect to $\ell$.

@@

\begin{lemma}\label{lem:calib-implies-indir}
	If a surrogate and link $(L, \psi)$ are calibrated with respect to a loss $\ell:\R \times\Y \to \reals$, then $L$ indirectly elicits the property $\gamma := \prop{\ell}$.
\end{lemma}
\begin{proof}
	Let $\Gamma$ be the unique property directly elicited by $L$, and fix $p \in \simplex$ with $u$ such that $p \in \Gamma_u$.
	As $p \in \Gamma_u$, then $\zeta(L(u;p) - \risk{L}(p)) = \zeta(0) = 0$, we observe the bound $\ell(\psi(u); p) \leq \ell(\gamma(p); p)$.
	We also have $\ell(\psi(u); p) \geq \risk{\ell}(p)$ by definition of $\risk{\ell}$, so we must have $\ell(\psi(u);p) = \risk{\ell}(p) = \ell(\gamma(p); p)$, and therefore, $p \in \gamma_{\psi(u)}$.
	Thus, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, so $L$ indirectly elicits $\gamma$.
\end{proof}

@@

\jessie{Need to redo this}
If we are just given the property $\gamma$ without a loss, assume that we have a sequence of measurable hypotheses $\{f_m\} \to f$ such that $\E_{(X,Y) \sim D} L(\psi \circ f_m(D_X), Y) \to \E_{(X,Y) \sim D} L(\gamma(D_X), Y)$.
We must then have $\E_X \mu(\gamma(D_X), \psi \circ f_m(X)) \to 0$ by consistency.
As in the proof of Proposition~\ref{prop:consistent-implies-calibrated}, this must be true for all $D_x$ for $x \in \X$, so we can abstract to distributions over $\simplex$.
Now, by consistency, we have the expected losses converging implies $\{\psi \circ f_m\}$ is converging toward the optimal hypothesis for all possible inputs $x \in \X$.

Let $\Gamma$ be the property directly elicited by $L$.
We have $\Gamma(D_x) = f(x)$ for all $x \in \X$, so we can see that the precedent being true implies $\mu(\psi \circ f_m(x), \gamma(p)) \to 0$ for all $p\in \simplex$.
As $\mu$ is a distance, $\mu(\psi \circ f(x), \Gamma(p)) = \mu(\psi \circ \Gamma(p), \gamma(p)) = 0$ for all $p \in \simplex$, which implies $\gamma = \psi \circ \Gamma$.
Therefore, $L$ must indirectly elicit the property $\gamma = \lim_{m \to \infty} \{\gamma_m\}$ via the link $\psi$.
\end{proof}

@@

\newpage
\appendix
\section{Omitted proofs}
\begin{proposition}
	When $\R$ is finite and $L$ continuous in $\reals^d$, calibration of a property via Definition~\ref{def:calibrated-general} implies calibration via Definition~\ref{def:calibrated-finite}.
	\jessie{eventually want iff}
\end{proposition}
\begin{proof}
	Let $\Gamma$ be the property elicited by $L$.
	We prove the contrapositive; if $(L, \psi)$ is not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then it is not calibrated via Definition~\ref{def:calibrated-general} either.

	Suppose there was a distribution $p \in \simplex$ and sequence $\{u_m\} \to u$ so that $\ell(\psi(u_m);p) \not \to \risk{\ell}(p)$ but $L(u_m;p) \to \risk{L}(p)$.
	We would then have $\inf_{u : \psi(u) \not \in \gamma(p)} L(u;p) = \inf_{u} L(u;p)$.

	We want to show that there is no $\zeta:\reals_+ \to \reals_+$ continuous at $0^+$ with $\zeta(0) = 0$ so that 
	\begin{align*}
	\ell(\psi(u);p) - \risk{\ell}(p) \leq \zeta(L(u;p) - \risk{L}(p))
	\end{align*}
	for all $u \in \reals^d$.
	We show that if this bound is satisfied, one of the two conditions on $\zeta$ (continuity at $0^+$ and $\zeta(0) = 0$) must be violated.

	First, suppose that $\zeta$ is continuous at $0^+$ and the bound is satisfied.
	Then for the sequence $\{u_m\} \to \Gamma(p)$, we have 
	\begin{align*}
	\lim_{m \to \infty}\ell(\psi(u_m); p) - \risk{\ell}(p)&\leq \lim_{m \to \infty} \zeta(L(u_m; p) - \risk{L}(p))\\
%	\lim_{m \to \infty}\ell(\psi(u_m) ; p) &\leq \risk{\ell}(p) + \lim_{m \to \infty} \zeta(L(u_m; p) - \risk{L}(p)\\
	\lim_{m \to \infty}\ell(\psi(u_m) ; p) &\leq \risk{\ell}(p) + \lim_{\epsilon \to 0^+} \zeta(\epsilon)~.~
	\end{align*}
	As $\lim_{m \to \infty} \ell(\psi(u_m);p) > \risk{\ell}(p)$, the last inequality can only happen if $\lim_{\epsilon \to 0^+} \zeta(\epsilon) = c > 0$, and by continuity of $\zeta$ at $0^+$, we must then have $\lim_{\epsilon \to 0^+} \zeta(\epsilon) = \zeta(0) = c > 0$.

%	Now, suppose $\zeta(0) = 0$, and take the sequence $\{u_m\} \to \Gamma(p)$ where $\psi(u_m) \neq \gamma(p)$ for all $m$.	
%	We have 
%	\begin{align*}
%	\lim_{m \to \infty}\ell(\psi(u_m); p) - \risk{\ell}(p)&\leq \lim_{m \to \infty} \zeta(L(u_m; p) - \risk{L}(p))\\
%	\lim_{m \to \infty}\ell(\psi(u_m); p) &\leq \risk{\ell}(p) +  \lim_{\epsilon \to 0^+} \zeta(\epsilon)\\
%%	\ell(\psi(\Gamma(p)); p) - \risk{\ell}(p)&\leq \zeta(\risk{L}(p) - L(\Gamma(p);p))\\
%%	\ell(\psi(\Gamma(p)); p) - \risk{\ell}(p)&\leq \zeta(0)\\
%%	\ell(\psi(\Gamma(p)); p) &\leq \zeta(0) + \ell(\gamma(p); p)\\
%%	\ell(\psi(\Gamma(p)); p) &\leq \ell(\gamma(p); p)~.~
%	\end{align*}
%	As $\ell(\psi(u_m); p)> \risk{\ell}(p)$ (since $\R$ is finite) for all $m$, we then observe that $\lim_{\epsilon \to 0^+} \zeta(\epsilon) = c > 0$.
%	However, since $\zeta(0) = 0$, we violate continuity of $\zeta$ at $0^+$.
\end{proof}

\begin{lemma}\label{lem:continuous-iff-limits}
	A function $\zeta:\reals \to \reals$ is continuous at $0$ and $\zeta(0) = 0$ if and only if the sequence $\{u_m\} \to 0 \implies \zeta(u_m) \to 0$.
\end{lemma}
\begin{proof}
	$\implies$ Suppose we have a sequence $\{u_m\} \to 0$.
	By continuity, we have $\lim_{u_m \to 0}\zeta(u_m) = \zeta(0) = 0$, so $\zeta(u_m) \to 0$.

	$\impliedby$ Suppose $\zeta(0) \neq 0$ but $\zeta$ was continuous at $0$.
	The constant sequence $\{u_m\} = 0$ then converges to $0$, but as $\zeta$ is continuous at $0$, we must have $\lim_{m \to \infty}\zeta(u_m) = \zeta(0) \neq 0$, so $\zeta(u_m) \not \to 0$.

	Now suppose $\zeta(0) = 0$ but $\zeta$ was not continuous at $0$.
	There must be a sequence $\{u_m\} \to 0$ so that $\lim_{m \to \infty}\zeta(u_m) \neq \zeta(0) = 0$, so $\zeta(u_m) \not \to 0$.
\end{proof}
